Democracy, Public Support, and Measurement Uncertainty

### 2021-01-11 paper/dcpo_demsupport.Rmd
revised 1201

# Discussion
In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and that democracy has a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.

>>>>

# Discussion
In short, the conclusions of Claassen [-@Claassen2020a; -@Claassen2020b] that public support has a positive effect on democracy and democracy a negative effect on support are not empirically supported once measurement uncertainty is taken into account, even when a superior estimate of public support and more data are used.
